Towards Transparency and Open Science

### 2023-02-06 manuscript.Rmd
de personified

The problem is that formal inductive reasoning can be part of an informal process.
A perfectly reproducible linear regression is, from the outside, indistinguishable from one that was cherry-picked from hundreds of possible regressions.
However, our expectations regarding verisimilitude and future performance between the cherry-picked and the simple regression should vary substantially.

>>>>

The problem is that formal inductive reasoning can be part of an informal process.
A perfectly reproducible linear regression is, from the outside, indistinguishable from one that was cherry-picked from hundreds of possible regressions.
However, the expectations regarding verisimilitude and future performance between the cherry-picked and the simple regression should vary substantially.
